Neural correlates of the deployment of spatial attention, and their modulation by repetitive movements

### 2024-09-29 manuscript.qmd
Added line numbers
Fixed typo

---
title: "Neural correlates of the deployment of spatial attention, and their modulation by repetitive movements"
author: 
  - name: Cameron Smith$^{1}$
  - name: Daniel H. Baker$^{1,2}$
bibliography: references.bib
csl: apa-6th-edition.csl
execute: 
  echo: false
  include: false
  output: false
format: pdf
---

@@

Future research should additionally pursue other avenues of exploration into the potential benefits of stimming. In this case, we focused on attention, given that this is a commonly reported area in which stimming generates benefits in individuals in autism [@Kapp2019] and there is crossover with fidgeting in ADHD, which is also reported to benefit attention [@Canela2017]. However, autistic individuals report a number of other benefits of stimming, for example emotional regulation [@Kapp2019; @Steward2015]. In order to obtain a full picture of the mechanisms and functions of stimming, to fully understand the behaviour and thus inform interventions which aim to reduce the behaviour, future research should investigate all reported avenues in which stimming may benefit.

>>>>

---
title: "Neural correlates of the deployment of spatial attention, and their modulation by repetitive movements"
author: 
  - name: Cameron Smith$^{1}$
  - name: Daniel H. Baker$^{1,2}$
bibliography: references.bib
csl: apa-6th-edition.csl
execute: 
  echo: false
  include: false
  output: false
format: pdf
header-includes: 
  \usepackage{lineno} \linenumbers
---

@@

Future research should additionally pursue other avenues of exploration into the potential benefits of stimming. In this case, we focused on attention, given that this is a commonly reported area in which stimming generates benefits in individuals with autism [@Kapp2019] and there is crossover with fidgeting in ADHD, which is also reported to benefit attention [@Canela2017]. However, autistic individuals report a number of other benefits of stimming, for example emotional regulation [@Kapp2019; @Steward2015]. In order to obtain a full picture of the mechanisms and functions of stimming, to fully understand the behaviour and thus inform interventions which aim to reduce the behaviour, future research should investigate all reported avenues in which stimming may benefit.
